---
title: "Section 3 Practice Question Solutions"
date: "June 13, 2023. (4:10pm-4:30pm)"
author: "TA: Kyle Gardiner<br>Tutors: Lina Li and  Jing Wang"
output: html_document
---


#### $(1)$ Loading in `College` dataset form the `ISLR2` package
```{r,message=FALSE}
library(ISLR2)
library(glmnet)
library(caret) 
data(College)
?College
```
\





#### $(2)$ Use `model.matrix()` to create design matrix where `Grad.Rate` is the outcome
```{r}
xx <- model.matrix(Grad.Rate ~., College) 
yy <- College$Grad.Rate
```
\

#### $(3)$ Splitting the data (NOTE: make sure to use 'set.seed(2023)')
```{r}
set.seed(2023)
id<-sample(nrow(Auto),round(nrow(Auto)*0.80)) 
xx.train<-xx[id,]
xx.test<-xx[-id,]
yy.train<-yy[id]
yy.test<-yy[-id]
```
\

#### $(4)$ Defining 10 fold cross validation using `trainControl()`
```{r}
cv_10 = trainControl(method = "cv", number = 10)
```
\



#### $(5)$ Using `train()` to build cross validation elastic net model
```{r}
elastic.net.cv = train(
  Grad.Rate ~.,       
  data = College[id,], 
  method = "glmnet",  
  trControl = cv_10) 

elastic.net.cv
```
\

#### $(6)$ Extracting best $\alpha$ and $\lambda$ from cross validation elastic net model
```{r}
myid <- order(elastic.net.cv$results$RMSE)[1] 

mybest.alpha <- elastic.net.cv$results$alpha[myid]
mybest.lambda <- elastic.net.cv$results$lambda[myid] 
```
\

#### $(7)$ Using the best $\alpha$ and $\lambda$ to build non-cv elastic net
```{r}
elastic.net.model<- glmnet(xx.train, yy.train, alpha = mybest.alpha, lambda = mybest.lambda)

coef(elastic.net.model)
```
\

#### $(8)$ Predicting values with `predict()`
```{r}
elastic.net.pred<-predict(elastic.net.model, s=mybest.lambda, newx=xx.test)
```
\


#### $(9)$ Calculating MSE
```{r}
mean((elastic.net.pred-yy.test)^2)
```

